Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-06-30 literature/paper_draft.qmd
an outline for literature review

In time series forecasting, aggregation occurs in a variety of settings. A concrete example of a hierarchy would be the Starbucks sales data, where their total sales is the sum of all countries they are operating in, and each national sales is the sum for all cities, and the sales for each city come from many outlets. Data on national tourism, electricity demand, or Gross Domestic Product (GDP) are similar examples of hierarchical time series. The impact of methods for forecasting hierarchical time series has not been limited to academia, with industry also showing a strong interest. Many companies have adopted these methods in practice, including Amazon, the International Monetary Fund, IBM, SAP, and more [@Athanasopoulos2024-as].

@@

## Hierarchical tructure

@@

$$
\tilde{\boldsymbol{y}}_{t+h|t} = \boldsymbol{S} \hat{\boldsymbol{b}}_{t+h|t} .
$$ {#eq-sb}

@@

$$
\tilde{\boldsymbol{y}}_{t+h|t} = \boldsymbol{S} \boldsymbol{G} \hat{\boldsymbol{y}}_{t+h|t},
$$ {#eq-sgy}

@@

$$
\hat{\boldsymbol{W}}^{shr}_{1} = \lambda_D \hat{\boldsymbol{W}}_{1, D} + (1 - \lambda_D) \hat{\boldsymbol{W}}_1,
$$

@@

$$
\hat{\lambda}_D = \frac{\sum_{i \neq j} \widehat{Var}(\hat{r}_{ij})} 
{\sum_{i \neq j} \hat{r}_{ij}^2}
$$

@@

-   $W_h$ is challenging to estimate, when $h>1$, we need alternative estimates.

For forecast errors $\hat{e}_{t|t-1}$, the unbiased sample covariance of in-sample one-step-ahead base forecast errors is:

$$
\hat{W}_1 = \frac{1}{T} \sum_{t=1}^{T} \hat{e}_{t|t-1} \hat{e}_{t|t-1}^{\top}.
$$

We reconstruct estimator of $W_h$ as $\hat{W}_h = k_h \, g(\hat{W}_1)$, where $k_h > 0$ simplifying the computation.

We will look into a few "sparse" + "non-sparse" approaches that apply on $\hat{W}_1$.

## The Shrinkage Estimator

$$
g(\hat{W}_1) = \hat{W}^{shr}_{1, D} = \lambda_D \hat{W}_{1, D} + (1 - \lambda_D) \hat{W}_1
$$ is the shrinkage estimator with diagonal target, proposed by Schäfer & Strimmer (2005). $\hat{W}_{1, D}$ is a diagonal matrix comprising the diagonal entries of $\hat{W}_1$. This approach will shrink the covariance matrix $\hat{W}_1$ towards its diagonal version, meaning the off-diagonal elements are shrunk towards zero while the diagonal ones remain unchanged.

They also proposed an optimal shrinkage intensity parameter $\lambda_D$ for this setting, assuming the variances are constant:

$$
\hat{\lambda}_D = \frac{\sum_{i \neq j} \widehat{Var}(\hat{r}_{ij})} {\sum_{i \neq j} \hat{r}_{ij}}
$$

where $\hat{r}_{ij}$ is the $ij$th element of $\hat{\boldsymbol{R}}_1$, the 1-step-ahead sample correlation matrix (obtained from $\hat{\boldsymbol{W}}_1$) to shrink it toward an identity matrix

-   (need more explanation on how to obtain optimal param)

-   Walkthrough the shrinkage estimator method

>>>>

In time series forecasting, aggregation occurs in a variety of settings. A concrete example of a hierarchy would be the Starbucks sales data, where their total sales is the sum of all countries they are operating in, and each national sales is the sum for all cities, and the sales for each city come from many outlets. Data on national tourism, electricity demand, or Gross Domestic Product (GDP) are similar examples of hierarchical time series. The impact of methods for forecasting hierarchical time series has not been limited to academia, with industry also showing a strong interest. Many companies have adopted these methods in practice, including Amazon, the International Monetary Fund, IBM, SAP, and more [@Athanasopoulos2024-as].
<!-- ##########  Literature Review  ########## -->

- Talk about the history and evolution of forecasting hierarchical time series, starting from the early heuristic methods to the modern statistical approaches.

  - Heuristic methods
  - Optimal combination methods (OLS, WLS)
  - MinT
  - Bayesian, Machine learning
  - Probabilistic methods

- Discuss the interests in MinT and how it has become a standard method for forecast reconciliation.

- Discuss the MinT's reliance on a good estimate of the covariance matrix of base forecast errors and other gaps

  - Empirical evidence of MinT under perform
  - Comparison with other methods

- Explain why this paper focus on exploring alternative covariance estimators for MinT. And is there any paper talk about this.

  - Is better estimate of W_h really lead to better performance?

- Talk about the paper outline and what will be covered in the following sections.

@@

## Hierarchical tructure {#sec-hierarchy}

@@

$$
\tilde{\boldsymbol{y}}_{t+h|t} = \boldsymbol{S} \hat{\boldsymbol{b}}_{t+h|t} \, .
$$ {#eq-sb}

@@

$$
\tilde{\boldsymbol{y}}_{t+h|t} = \boldsymbol{S} \boldsymbol{G} \hat{\boldsymbol{y}}_{t+h|t} \; ,
$$ {#eq-sgy}

@@

$$
\hat{\boldsymbol{W}}^{shr}_{1} = \lambda_D \hat{\boldsymbol{W}}_{1, D} + (1 - \lambda_D) \hat{\boldsymbol{W}}_1 \, ,
$$

@@

$$
\hat{\lambda}_D = \frac{\sum_{i \neq j} \widehat{Var}(\hat{r}_{ij})} 
{\sum_{i \neq j} \hat{r}_{ij}^2} \, ,
$$

@@
